---
title: "steps.Rmd"
output: html_document
---

Exercise for Coursera "Reproducible Research"

Read in the source data:
```{r}
activity<-read.csv("activity/activity.csv")
source("steps.R")
```

##What is mean total number of steps taken per day?

Histogram of total steps per day

```{r}
activityHistByDay(activity)
```

Mean and Median of average steps per day

```{r}
activityMeanAndMedian(activity)
```

##What is the average daily activity pattern?

Plot of average steps per interval

```{r}
activityPlotByInterval(activity)
```

Which interval has greatest average?

```{r}
activityWhichMax(activity)
```

##Inputing missing values

How many incomplete rows?

```{r}
sum(!complete.cases(activity))
```

Fill incomplete rows using averages for intervals

```{r}
activitymod <- activityFillNAs(activity)
```


Histogram of total steps per day - incomplete rows filled

```{r}
activityHistByDay(activitymod)
```

Mean and Median of total steps per day - incomplete rows filled

```{r}
activityMeanAndMedian(activitymod)
```

##Are there differences in activity patterns between weekdays and weekends?

Set Weekend / weekday as "dayType""

```{r}
activitymod<-setDayTypes(activitymod)
```

Plot of average steps per interval for Weekdays - incomplete rows filled

```{r}
activityPlotByInterval(activitymod[activitymod[4]=="weekday",])
```


Plot of average steps per interval for Weekends - incomplete rows filled

```{r}
activityPlotByInterval(activitymod[activitymod[4]=="weekend",])
```

